---
output: github_document
---

```{r, echo = FALSE}
version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])
version <- gsub('-', '.', version)
```

[![R-CMD-check](https://github.com/tsmodels/tsets/workflows/R-CMD-check/badge.svg)](https://github.com/tsmodels/tsets/actions)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/tsets)](https://cran.r-project.org/package=tsets)


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tsets
Single source of error based state space models (exponential smoothing) including 
the power MAM model, normalized seasonality and ability to include regressors in 
the observation equation. Part of a unified time series framework using methods 
and classes from tsmethods. Estimation supports automatic differentiation via the
TMB package.

Since v.1.9.0, missing values are automatically handled via the prediction/update 
step during estimation.

## Installation

For installation instructions and vignettes for **tsmodels** packages, 
see https://tsmodels.github.io/.
